---
title: "Unit Test Practice"
format: html
editor: visual
---

## Unit testing with the `testtthat` package

First, intall necessary packages
```{r}
#install.packages("testthat")
#install.packages("devtools")
#install.packages("remotes")

library(testthat)
library(devtools)
library(remotes)
```
Write a function to practice unit tests.

This function is going to find the mean value of each column, and then return the lowest and highest mean value calculated ( in that order)

We would expect:
- the output to be numeric
- output should be a vector of length 2
- the first value should be smaller than the second value
```{r}
mean_range <- function(df) {
  col_means <- apply(X = df, MARGIN = 2, FUN = mean, na.rm = TRUE)
  col_mean_max <- max(col_means)
  col_mean_min <- min(col_means)
  
  # return min and max values (in that order)
  return(c(col_mean_min, col_mean_max))
}

mean_range(df = mtcars)
```
Write some unit tests!
```{r}
#| include: false
# Test that the output is of length 2
expect_length(mean_range(df = mtcars), 2)
```

